Data preparation report

### 2023-06-15 00_dataPrepReport.Rmd
Re-downloaded data including the 2023 breeding season

```{r download-movebank-data}
# base::load("movebankCredentials/pw.Rda")
# MB.LoginObject <- move::movebankLogin(username = "kaijagahm", password = pw)
# rm(pw)
minDate <- "2020-09-01 00:00"
maxDate <- "2022-12-15 11:59"
#dat <- vultureUtils::downloadVultures(loginObject = MB.LoginObject, removeDup = T, dfConvert = T, quiet = T, dateTimeStartUTC = minDate, dateTimeEndUTC = maxDate)
#write_feather(dat, "data/dat.feather")
dat <- read_feather("data/dat.feather")
```

>>>>

```{r download-movebank-data}
# base::load("movebankCredentials/pw.Rda")
# MB.LoginObject <- move::movebankLogin(username = "kaijagahm", password = pw)
# rm(pw)
minDate <- "2020-09-01 00:00"
maxDate <- "2023-05-15 11:59"
dat <- vultureUtils::downloadVultures(loginObject = MB.LoginObject, removeDup = T, dfConvert = T, quiet = T, dateTimeStartUTC = minDate, dateTimeEndUTC = maxDate)
write_feather(dat, "data/dat.feather")
dat <- read_feather("data/dat.feather")
```
